---
title: "Introduction to afnews"
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{Introduction to afnews}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(afnews)
knitr::opts_chunk$set(
  comment = "#>", 
  collapse = TRUE
)
```

There are three main families of functions in afnews:

1. General tools: these functions allow you to check the existence of a web url in https, htpp or not. They also allow to set tables, vector, matrices of different sizes (columns).

2. Function of collecting articles on many press.

3. Main functions of collecting news from articles collected or urls provided.



## General tools


* You can verify the existence of a URL with  `url_exists()`:

```{r}
url_exists("https://armelsoubeiga.github.io/afnews/index.html",non_2xx_return_value = FALSE, quiet = FALSE)
```

This returns TRUE if the url in parameter exists. The function also checked the HTTP code is not in the range `2xx`, the default is to return <<FALSE>>.

* You can also merge r objects (chars, int, data.frame, ...) of different sizes through the `cbind_na ()` function:

Note that the plus or minus lines are replaced by NA.



